### 2021-04-11 Paper.tex
modified

\section{Introduction}\label{sec:intro}
PROVAThis supplement includes a description of the code, with a presentation of the features implemented followed by results of extensive benchmarks listed in Table \ref{tab:list}, implemented to verify that the code solves correctly a large range of problems. Description and results of the benchmarks are shown in Section \ref{sec:benchmark}.

>>>>

\section{Introduction}\label{sec:intro}
This supplement includes a description of the code, with a presentation of the features implemented followed by results of extensive benchmarks listed in Table \ref{tab:list}, implemented to verify that the code solves correctly a large range of problems. Description and results of the benchmarks are shown in Section \ref{sec:benchmark}.
